Generative Synthesis of Insurance Datasets

### 2020-06-19 manuscript/manuscript.Rmd
revisions

---
title: Generative Synthesis of Insurance Datasets
authors:
  - name: Kevin Kuo
    affiliation: RStudio, Kasa AI
    email: kevin@kasa.ai
abstract: |
  One of the impediments in advancing actuarial research and developing open 
  source assets for insurance analytics is the lack of realistic publicly
  available datasets. In this work, we develop a workflow for synthesizing
  insurance datasets leveraging current neural network techniques. We 
  evaluate the predictive modeling efficacy of datasets synthesized from
  publicly available data in the domains of general insurance pricing and life
  insurance shock lapse modeling. The trained synthesizers are able to capture
  representative characteristics of the real datasets. This workflow is 
  implemented via an R interface to promote adoption by researchers and data
  owners.
keywords:
  - synthetic data
  - generative adversarial networks
  - actuarial science
bibliography: manuscript
# bibliographystyle: abbrvnat
header-includes: |
  \usepackage{makecell}
  \usepackage{amsmath}
  \usepackage[numbers]{natbib}
  \bibliographystyle{abbrvnat}
  \usepackage{graphicx}
  \usepackage{mathtools}
  \usepackage{lmodern}
output: 
  bookdown::pdf_book:
    base_format: rticles::arxiv_article
    citation_package: natbib
---

@@

Our workflow is based on the CTGAN architecture with some modifications. As of 
the writing of this paper, CTGAN represents the 
state-of-the-art for synthesizing tabular data [@xuModelingTabular2019].
In this section, we provide a brief overview of GANs, the extensions of GAN that
CTGAN proposes in order to train
quality generative models for tabular data, and modifications we introduce to
adopt the architecture for insurance datasets. We remark that neural network rudiments 
have been discussed extensively in the actuarial literature (see, for example, the survey by
@richman2018ai, the lecture notes by @wuthrich2019data, and references therein)
and will not be covered here.

@@

Again, in Equation \@ref(eq:gan), the critic $C$ aims to maximize the score it assigns to
instances from the real data samples, while the generator $G$ maximize the score
given by the critic to the samples it generates. In practice, we alternately optimize
the two networks, fixing one while training the other. Once the generator and 
critic networks have been trained, one can input samples of
$Z$ into the generator $G$ to obtain synthesized instances.

@@

@@

```{r metrics, echo=FALSE, message=FALSE, fig.cap="Box plots of cross-validated performance of models trained on real and synthetic data for the two case studies.", fig.width=5, fig.height=3, fig.pos='H'}
library(tidyverse)
tpl_rmse <- readRDS("data/tpl.rds")
shock_lapse_rmse <- readRDS("data/shock_lapse.rds")
bind_rows(`TPL Frequency` = tpl_rmse, 
          `Shock Lapse` = shock_lapse_rmse, 
          .id = c("Dataset")) %>% 
  rename(synthetic = rmse_syn,
         real = rmse_train) %>% 
  mutate(fold = row_number()) %>% 
  pivot_longer(c("synthetic", "real"), names_to = "model") %>% 
  ggplot(aes(y = value, x = model)) + 
  geom_boxplot(
    size = 0.25, outlier.size = 0.5
    ) +
  facet_wrap(~ Dataset, ncol = 1, scales = "free_x") +
  ylim(c(0, NA)) +
  xlab("Model Training Data") +
  ylab("Assessment RMSE") +
  coord_flip() +
  theme_bw()
```

@@

>>>>

---
title: Generative Synthesis of Insurance Datasets
authors:
  - name: Kevin Kuo
    affiliation: RStudio, Kasa AI
    email: kevin@kasa.ai
abstract: |
  One of the impediments in advancing actuarial research and developing open 
  source assets for insurance analytics is the lack of realistic publicly
  available datasets. In this work, we develop a workflow for synthesizing
  insurance datasets leveraging CTGAN, a recently proposed neural network
  architecture for generating tabular data. Applying the proposed workflow to
  publicly available data in the domains of general insurance pricing and life
  insurance shock lapse modeling, we evaluate the synthesized datasets from a
  few perspectives: machine learning efficacy, distributions of variables, and
  stability of model parameters. This workflow is 
  implemented via an R interface to promote adoption by researchers and data
  owners.
keywords:
  - synthetic data
  - generative adversarial networks
  - actuarial science
bibliography: manuscript
# bibliographystyle: abbrvnat
header-includes: |
  \usepackage{makecell}
  \usepackage{amsmath}
  \usepackage[numbers]{natbib}
  \bibliographystyle{abbrvnat}
  \usepackage{graphicx}
  \usepackage{mathtools}
  \usepackage{lmodern}
output: 
  bookdown::pdf_book:
    base_format: rticles::arxiv_article
    citation_package: natbib
---

@@

Our workflow is based on the CTGAN architecture with some modifications. As of 
the writing of this paper, CTGAN represents the 
state-of-the-art for synthesizing tabular data [@xuModelingTabular2019].
In this section, we provide a cursory overview of GANs, the extensions of GAN that
CTGAN proposes in order to train
quality generative models for tabular data, and modifications we introduce to
adopt the architecture for insurance datasets. We remark that neural network rudiments 
have been discussed extensively in the actuarial literature (see, for example, the survey by
@richman2018ai, the lecture notes by @wuthrich2019data, and references therein)
and will not be covered here.

@@

Again, in Equation \@ref(eq:gan), the critic $C$ aims to maximize the score it assigns to
instances from the real data samples, while the generator $G$ maximize the score
given by the critic to the samples it generates. In practice, we alternately optimize
the two networks, fixing one while training the other. Once the generator and 
critic networks have been trained, one can input samples of
$Z$ into the generator $G$ to obtain synthesized instances. For more details on GAN,
we refer the user to @NIPS2014_5423.

@@

In this section, we present and discuss the results of our experiments. The main findings are 
as follows:

1. In terms of cross-validation performance, the models trained using the synthetic
datasets perform similarly to those trained using the real datasets;
2. The distribution of variables, both continuous and categorical, in the synthetic
datasets are consistent with those in the real datasets; however,
3. The relativities of GLM models built on the synthetic datasets *do not* exhibit
similar patterns to those of models built on real datasets.

@@

```{r metrics, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Box plots of cross-validated performance of models trained on real and synthetic data for the two case studies.", fig.width=5, fig.height=3, fig.pos='H'}
library(tidyverse)
tpl_rmse <- readRDS("data/tpl.rds")
shock_lapse_rmse <- readRDS("data/shock_lapse.rds")
bind_rows(`TPL Frequency` = tpl_rmse, 
          `Shock Lapse` = shock_lapse_rmse, 
          .id = c("Dataset")) %>% 
  rename(synthetic = rmse_syn,
         real = rmse_train) %>% 
  mutate(fold = row_number()) %>% 
  pivot_longer(c("synthetic", "real"), names_to = "model") %>% 
  ggplot(aes(y = value, x = model)) + 
  geom_boxplot(
    size = 0.25, outlier.size = 0.5
    ) +
  facet_wrap(~ Dataset, ncol = 1, scales = "free_x") +
  ylim(c(0, NA)) +
  xlab("Model Training Data") +
  ylab("Assessment RMSE") +
  coord_flip() +
  theme_bw()
```

@@

```{r, echo=FALSE, cache=TRUE, warning=FALSE}
combined <- read_csv("data/actual_and_synthesized_data.csv",
                     col_types = cols(
  num_claims = col_integer(),
  exposure = col_double(),
  area = col_character(),
  vehicle_power = col_character(),
  vehicle_age = col_character(),
  driver_age = col_character(),
  bonus_malus = col_double(),
  vehicle_brand = col_character(),
  vehicle_gas = col_character(),
  density = col_double(),
  region = col_character(),
  dataset = col_character()
))

make_bar <- function(dataset, variable) {
  dataset %>% 
    ggplot(aes(x = !!sym(variable))) +
    geom_bar() +
    facet_wrap(~dataset) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}

make_histogram <- function(dataset, variable, binwidth = 10) {
  dataset %>% 
    ggplot(aes(x = !!sym(variable))) +
    geom_histogram(binwidth = binwidth) +
    facet_wrap(~dataset) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}

make_scatter <- function(dataset, variable) {
  c("actual", "synthesized") %>% 
    map_dfc(~ dataset %>% 
              filter(dataset == .x) %>% 
              select(!!sym(.x) := !!sym(variable))) %>% 
    mutate_all(sort) %>% 
    ggplot(aes(x = actual, y = synthesized)) +
    xlab(paste0("actual ", variable)) +
    ylab(paste0("synthesized ", variable)) +
    geom_point() +
    theme_bw()
}

results <- readRDS("data/result.rds")

extract_relativities <- function(res) {
  coef_glm_syn <- res %>% 
    map_dfr("coef_glm_syn") %>% 
    mutate(relativity = exp(estimate),
           dataset = "synthesized")
  coef_glm_train <- res %>% 
    map_dfr("coef_glm_train") %>% 
    mutate(relativity = exp(estimate),
           dataset = "real")

  coefs <- bind_rows(
    coef_glm_syn,
    coef_glm_train
  ) %>% 
    tidyr::separate("term", into = c("variable", "level"),
                    sep = "(?<=[a-z])(?=[0-9]|[A-Z]|<|>|\\[)")

  coefs %>% 
    select(variable, level, relativity, dataset)
}
coefs <- extract_relativities(results)
```

In Figures \ref{fig:distribution-area}, \ref{fig:distribution-bonus-malus}, and
\ref{fig:distribution-region}, we compare distributions of select variables from 
a synthesized sample of the TPL datasets with their distributions from the real 
dataset. We note that, qualitatively, the synthesized distributions exhibit realistic
patterns.

```{r distribution-area, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Distributions of the Area variable.", fig.width=6, fig.height=2}
make_bar(combined, "area")
```

```{r distribution-bonus-malus, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Distributions of the Bonus/Malus variable.", fig.width=6, fig.height=2}
make_histogram(combined, "bonus_malus")
```

```{r distribution-region, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Distributions of the Region variable.", fig.width=6, fig.height=2}
make_bar(combined, "region")
```

In terms of model relativities, we see a divergence of patterns between the synthetic
and real datasets. In Figures  \ref{fig:relativities-area}, \ref{fig:relativities-bonus-malus}, and \ref{fig:relativities-region}, 
we plot the 
relativities of select variables from
models trained during 10-fold cross-validation. We see that the trends are noticeably
different and that the variances of the relativities resulting from models fitted
on the synthetic datasets are larger than those resulting from models fitted on the
corresponding folds of the real dataset.

These explorations, which we recommend users perform on their datasets of interest,
enable them to form an initial assessment on whether the workflow
is appropriate for their use cases. For example, in our case, due to the instability
of GLM parameters, it may not be advisable to develop a rating plan using the synthesized
data. However, it may be appropriate to use the synthesized dataset to demonstrate 
a procedure for developing such a plan.

We note that we do not perform hyperparameter tuning of CTGAN in these experiments,
so results could potentially be improved if dataset-specific tuning is performed.

```{r relativities-area, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Relativities of the Area  variable across cross-validated models", fig.width=6,fig.height=2}
coefs %>% 
  filter(!is.na(level)) %>% 
  filter(variable == "area") %>% 
  ggplot(aes(x = level, y = relativity, color = dataset)) +
  geom_boxplot() +
  theme_bw() +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red")
```

```{r relativities-bonus-malus, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Relativities of the Bonus/Malus  variable across cross-validated models", fig.width=6,fig.height=2}
coefs %>% 
  filter(is.na(level)) %>% 
  filter(variable == "bonus_malus") %>% 
  ggplot(aes(y = relativity, x = level, color = dataset)) +
  theme_bw() +
  geom_boxplot() +
  theme(axis.title.x=element_blank(),
       axis.text.x=element_blank(),
       axis.ticks.x=element_blank()) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red")
```

```{r relativities-region, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Relativities of the Region  variable across cross-validated models", fig.width=6,fig.height=2}
coefs %>% 
  filter(!is.na(level)) %>% 
  filter(variable == "region") %>% 
  ggplot(aes(x = level, y = relativity, color = dataset)) +
  geom_boxplot() +
  theme_bw() +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
